Group 1: Tennis 

### 2019-12-11 Group1Prez.Rmd
Fixed mens data

## Tournament Results: Men
```{r, echo=FALSE}
Tourney1_Men = data.frame(`P(Winning a Rally)` = TDMen[,1],
                            `Paper P(Winning the Tournement)` = c(.2872, .3599, .0482, .3074))
#`Our P(Winning the Tournement )` =round( pTC(TDMen[1,1],TDMen[2,1],TDMen[3,1],TDMen[4,1], 2), 4)

>>>>

## Tournament Results: Men
```{r, echo=FALSE}
Tourney1_Men = data.frame(`P(Winning a Rally)` = TDMen[,1],
                            `Paper P(Winning the Tournement)` = c(.6747, .0851, .0945, .1457))
#`Our P(Winning the Tournement )` =round( pTC(TDMen[1,1],TDMen[2,1],TDMen[3,1],TDMen[4,1], 2), 4)
